---
title: "Report"
output:
  html_document
params:
  group: group
---


```{r packages, echo=FALSE, include =FALSE}
library(heatmaply)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(htmltools)
options(tinytex.verbose = TRUE)
```


# General information.

## Mapping quality.

```{r mapping quality, echo=FALSE,out.width = '100%', message=FALSE}
file = paste0("../Results/General_Plots/Quality_barplot_", params$group, ".jpeg")
knitr::include_graphics(file) 
```

## Reads per sample.

```{r reads per sample, echo=FALSE, out.width = '66%', message=FALSE}
file = paste0("../Results/General_Plots/Barplot_reads_", params$group, ".jpeg")
knitr::include_graphics(file) 
```


## Counts per tRNA isoacceptor.

```{r isoacceptor, echo=FALSE, out.width = '100%', message=FALSE}
file = paste0("../Results/Counts_Plots/Total/", params$group, "_by_Isoacceptor.jpeg")
knitr::include_graphics(file) 
```

## Counts per tRNA isodecoder.

```{r isodecoder, echo=FALSE, out.width = '100%'}
file = paste0("../Results/Counts_Plots/Total/", params$group, "_by_Isodecoder.jpeg")
knitr::include_graphics(file) 
```



# Alanine.

```{r counts, echo=FALSE, out.width = '100%'}
aa = "Ala"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```


## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Arginine.

```{r counts2, echo=FALSE, out.width = '100%'}
aa = "Arg"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 

```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Asparagine.

```{r counts4, echo=FALSE, out.width = '100%'}
aa = "Asn"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Aspartic acid.

```{r counts3, echo=FALSE, out.width = '100%'}
aa = "Asp"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)



# Cysteine

```{r counts5, echo=FALSE, out.width = '100%'}
aa = "Cys"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Glutamine

```{r counts6, echo=FALSE, out.width = '100%'}
aa = "Gln"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Glutamic acid

```{r counts7, echo=FALSE, out.width = '100%'}
aa = "Glu"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Glycine

```{r counts8, echo=FALSE, out.width = '100%'}
aa = "Gly"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Histidine

```{r counts9, echo=FALSE, out.width = '100%'}
aa = "His"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Isoleucine

```{r counts10, echo=FALSE, out.width = '100%'}
aa = "Ile"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Leucine

```{r counts12, echo=FALSE, out.width = '100%'}
aa = "Leu"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)



# Lysine

```{r counts13, echo=FALSE, out.width = '100%'}
aa = "Lys"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Methionine

```{r counts14, echo=FALSE, out.width = '100%'}
aa = "Met"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# iMethionine

```{r counts11, echo=FALSE, out.width = '100%'}
aa = "iMet"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)



# Phenylalanine

```{r counts15, echo=FALSE, out.width = '100%'}
aa = "Phe"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Proline

```{r counts16, echo=FALSE, out.width = '100%'}
aa = "Pro"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Selenocysteine

```{r counts17, echo=FALSE, out.width = '100%'}
aa = "SeC"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)



# Serine

```{r counts18, echo=FALSE, out.width = '100%'}
aa = "Ser"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Threonine

```{r counts19, echo=FALSE, out.width = '100%'}
aa = "Thr"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Tryptophan

```{r counts20, echo=FALSE, out.width = '100%'}
aa = "Trp"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Tyrosine

```{r counts21, echo=FALSE, out.width = '100%'}
aa = "Tyr"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 
heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)


# Valine

```{r counts22, echo=FALSE, out.width = '100%'}
aa = "Val"
file = paste0("../Results/Counts_Plots/Total/By_tRNA_family/", params$group, "_", aa, "_by_family.jpeg")
knitr::include_graphics(file) 

file2 = paste0("../Results/Counts_Plots/Processed_vs_Precursor/By_tRNA_family/", params$group,"_", aa, "_by_family.jpeg")
knitr::include_graphics(file2) 

heatmap_url = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, ".html")
heatmap_url_high_coverage = paste0("../Modification_Coverage/Modification_Heatmaps_Plots/", params$group, "_heatmap_", aa, "_high_coverage.html")

file3 = paste0("../Results/Modification_Coverage/Coverage_Plots/", params$group,"_Coverage_", aa, ".jpeg")
knitr::include_graphics(file3) 
```

## [Modification analysis](`r heatmap_url`)

### [Filter low coverage](`r heatmap_url_high_coverage`)

# Mitochondrial tRNAs or mitochondrial tRNA-lookalike nuclear sequences.

```{r counts23, echo=FALSE, out.width = '100%'}
file = paste0("../Results/Counts_Plots/Total/", params$group, 
              "_mitochondrialtRNA.jpeg")
knitr::include_graphics(file) 
```
