---
title: "Comparison"
output:
  html_document
    #number_sections: TRUE
params:
  group: group
---


```{r packages, echo=FALSE, include =FALSE}
library(heatmaply)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(htmltools)
options(tinytex.verbose = TRUE)
```


# General information.

## PCA.

```{r PCA, echo=FALSE, out.width = '100%'}
file = paste0("../Results/Plots/PCA_plot.jpeg")
knitr::include_graphics(file) 
```

## Mapping quality.

```{r mapping quality, echo=FALSE,out.width = '100%'}
file2 = paste0("../Results/Plots/Quality_barplot.jpeg")
knitr::include_graphics(file2) 
```

## Reads per sample.

```{r reads per sample, echo=FALSE, out.width = '100%'}
file3 = paste0("../Results/Plots/Barplot_reads_total.jpeg")
knitr::include_graphics(file3) 
```


## Mature ratio.

### Comparison between groups.

```{r mature ratio group, echo=FALSE, out.width = '100%'}
file31 = paste0("../Results/Counts_plots/Mature_vs_Precursor/Comparison_by_group.jpeg")
knitr::include_graphics(file31) 
```

### Isoacceptor level.

```{r mature ratio isoaccpetr, echo=FALSE, out.width = '100%'}
file32 = paste0("../Results/Counts_plots/Mature_vs_Precursor/Comparison_by_isoacceptor.jpeg")
knitr::include_graphics(file32) 
```


# Differential expression. 

## Counts per tRNA isoacceptor.

```{r isoacceptor, echo=FALSE, out.width = '100%'}
file4 = paste0("../Results/Counts_plots/Total/Total_by_Isoacceptor.jpeg")
knitr::include_graphics(file4) 
```

```{r MD plot isoaceptor, echo=FALSE, out.width = '100%'}
md_plot_deseq = paste0("../DEG/DESeq2_MD-plot_isoaceptors.html")
```

### [Differential analysis by isoaceptor](`r md_plot_deseq`)


## Counts per tRNA isodecoder.

```{r isodecoder, echo=FALSE, out.width = '100%'}
file5 = paste0("../Results/Counts_plots/Total/Total_by_Isodecoder.jpeg")
knitr::include_graphics(file5) 
```

```{r MD plot isodecoder, echo=FALSE, out.width = '100%'}
md_plot_deseq = paste0("../DEG/DESeq2_MD-plot_isodecoders.html")
```

### [Differential analysis by isodecoder](`r md_plot_deseq`)

## Analysis of all tRNA genes.

```{r MD plot DESeq2, echo=FALSE, out.width = '100%'}
md_plot_deseq = paste0("../DEG/DESeq2_MD-plot_all_genes.html")
```

### [DESeq2](`r md_plot_deseq`)

### Heatmap by group.
```{r Heatmap groups, echo=FALSE, out.width = '100%'}
file7 = paste0("../Results/DEG/Heatmap_groups_all_genes_DESeq2.jpeg")
knitr::include_graphics(file7) 
```


```{r MD plot iso-trna-cp, echo=FALSE, out.width = '100%'}
md_plot_iso = paste0("../DEG/Results_iso-tRNA-CP.html")
```


### [iso-tRNA-CP](`r md_plot_iso`)

### Heatmap by group.
```{r Heatmap groups iso, echo=FALSE, out.width = '100%'}
file9 = paste0("../Results/DEG/Heatmap_groups_isotRNACP.jpeg")
knitr::include_graphics(file9) 
```


# Modification analysis

```{r Mod analysis1, echo=FALSE, out.width = '100%'}
aa = "Ala"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Alanine](`r heatmap_url_mod`)

```{r Mod analysis2, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Arg"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Arginine](`r heatmap_url_mod`)

```{r Mod analysis3, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Asn"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Asparagine](`r heatmap_url_mod`)

```{r Mod analysis4, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Asp"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Aspartic acid](`r heatmap_url_mod`)

```{r Mod analysis5, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Cys"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Cysteine](`r heatmap_url_mod`)

```{r Mod analysis6, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Gln"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Glutamine](`r heatmap_url_mod`)

```{r Mod analysis7, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Glu"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Glutamic acid](`r heatmap_url_mod`)

```{r Mod analysis8, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Gly"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Glycine](`r heatmap_url_mod`)

```{r Mod analysis9, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "His"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Histidine](`r heatmap_url_mod`)

```{r Mod analysis10, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Ile"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Isoleucine](`r heatmap_url_mod`)

```{r Mod analysis11, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Leu"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Leucine](`r heatmap_url_mod`)

```{r Mod analysis12, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Lysine"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Lysine](`r heatmap_url_mod`)

```{r Mod analysis13, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Met"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Methionine](`r heatmap_url_mod`)

```{r Mod analysis14, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "iMet"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [iMethionine](`r heatmap_url_mod`)

```{r Mod analysis15, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Phe"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Phenylalanine](`r heatmap_url_mod`)

```{r Mod analysis16, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Pro"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Proline](`r heatmap_url_mod`)

```{r Mod analysis17, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "SeC"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Selenocysteine](`r heatmap_url_mod`)

```{r Mod analysis18, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Ser"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Serine](`r heatmap_url_mod`)

```{r Mod analysis19, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Thr"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Threonine](`r heatmap_url_mod`)

```{r Mod analysis20, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Trp"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Tryptophan](`r heatmap_url_mod`)

```{r Mod analysis21, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Tyr"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Tyrosine](`r heatmap_url_mod`)

```{r Mod analysis22, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}

aa = "Val"
heatmap_url_mod = paste0("../Heatmaps/Comparison_", aa, ".html")
```

## [Valine](`r heatmap_url_mod`)

```{r Mod analysis23, echo=FALSE, out.width = '100%'}
file = paste0("../Results/", substr(heatmap_url_mod,4,nchar(heatmap_url_mod)))
if(!file.exists(file)){
  text = paste0("There is no significant modification on ", aa, " genes")
  print(text)
}
```
